Alien species

### 2023-09-28 alien_species.Rmd
Update threhold value #38
Change _Økologisk egenskap_ assignment #86

March 2023

@@

```{r, echo=F}
Ecosystem <- "Våtmark, Naturlig åpne områder under skoggrensa, Semi-naturlig mark" 
Egenskap  <- "Funksjonelt viktige arter og strukturer"
ECT       <- "B1 Compositional state characteristics" 
Contact   <- "anders.kolstad@nina.no"
```

@@

Upper reference value is then 1, and lower reference value is 7, on the R7 scale.
For the threshold value I will set this to value 4 on the R7 scale. 
This is based on interpretation by the author and based of the definition of this value in Fig. \@ref(fig:R7). 
Step 4 on the R7 scale is the step that, concordantly, best matches the 5% threshold in the old approach, as seen from Fig. \@ref(fig:fremmedart-prosentVSinnslag).

@@

The indicator is tagged to the *Økologisk egenskap* called
**Funksjonelt viktige arter og strukturer** (Functionally important species and structures). This emphasises the negative effect that alien species have on for example supressing or excluding native species. In some cases, alien species can also affect nutrient cycling or recruitment.

@@

* Threshold = 4 (R7 scale), corresponding to about 5-30% alien species cover.

@@

@@

```{r}
low <- 1
high <- 7
threshold <- 4
```

>>>>

September 2023

@@

```{r, echo=F}
Ecosystem <- "Våtmark, Naturlig åpne områder under skoggrensa, Semi-naturlig mark" 
Egenskap  <- "Biologisk mangfold"
ECT       <- "B1 Compositional state characteristics" 
Contact   <- "anders.kolstad@nina.no"
```

@@

Upper reference value is then 1, and lower reference value is 7, on the R7 scale.
For the threshold value I will set this to value 3 on the R7 scale. 
This is based on interpretation by the author and based of the definition of this value in Fig. \@ref(fig:R7). 
Step 3 on the R7 scale is the step that, concordantly, best matches the 5% threshold in the old approach, as seen from Fig. \@ref(fig:fremmedart-prosentVSinnslag).

@@

The indicator is tagged to the *Økologisk egenskap* called
**Biologisk mangfold**. 
This emphasises the negative effect that alien species have on for example supressing or excluding native species. 
In some cases, alien species can also affect nutrient cycling or recruitment and could then also be appropriate under _funksjonelt viktige arter og strukturer_.

@@

* Threshold = 3 (R7 scale), corresponding to about 2-5% alien species cover.

@@

For a discussion around the reference values, see [here](https://github.com/NINAnor/ecosystemCondition/issues/38)

@@

```{r}
low <- 1
high <- 7
threshold <- 3
```
